Sampling-Based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex
cont

The generation of the random samples directly influences the performance of the RRT-based planners.
In classic RRT, the random samples are drawn uniformly in the whole configuration space, which leads to the well known narrow passage problem.
The void space can be considered as a narrow passage, as the movement of the probe is constrained by many atoms.
The limitation is even higher for larger probes.
To boost the growth of the tree inside the narrow void space, the random samples can be generated around places that are believed to be a part of the collision-free region $\CF^i$.
This region is approximated by the Voronoi vertices $\VV^i$ and the random samples can be generated around them.

However, the probability of sampling cannot be increased around all Voronoi vertices at once, because the growth of the tree towards the Voronoi vertices may be blocked by the obstacles (atoms)~\cite{vonasekphd}.
It is necessary to guide the growth of the tree by increasing the probability of sampling only around such Voronoi vertices that can be reached by the tree with a higher probability.
Such Voronoi vertices have to be located close to the tree.
Therefore, a subset $\VVA^i \subseteq \VV^i$ of the Voronoi vertices that are close to the tree is maintained (Alg.~\ref{alg::update}).
A Voronoi vertex $v \in \VV^i$ is considered as active if the distance to its nearest node in the tree is less than $\da$, but larger than
$\db$.
After the update of $\VVA^i$, the tree attempts to expand towards them (Alg.~\ref{alg::main}, line~\ref{alg::main::d}--\ref{alg::main::e}).
This expansion is not always successfull, especially for distant Voronoi vertices, but it helps the tree to explore the void space.

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{fig/caver3450-3700_colored}
\caption{\label{fig::caver34}
Visualization of tunnels detected using our method (RRT) in comparison to tunnels detected by CAVER.
Both static tunnels detected by CAVER and by our method are depicted in gray.
Then, colored bars show snapshots where a dynamic tunnel was detected by our algorithm.
The dynamic tunnel bars are colored according to the order in which a snapshot occurs in the dynamic tunnel.
It is visible that our method is able to extract many additional information about the void space than traditional static tunnels computed by CAVER.
}
\end{figure}

>>>>

The generation of the random samples directly influences the performance of the RRT-based planners.
In classic RRT, the random samples are drawn uniformly in the whole configuration space, which leads to the narrow passage problem.
The void space can be considered as a narrow passage, as the movement of the probe is constrained by many atoms.
The limitation is even higher for larger probes.
To boost the growth of the tree inside the narrow void space, the random samples can be generated around places that are believed to be a part of the collision-free region $\CF^i$.
This region is approximated by the Voronoi vertices $\VV^i$ and the random samples can be generated around them.

However, the probability of sampling cannot be increased around all Voronoi vertices at once, because the growth of the tree towards the Voronoi vertices may be blocked by the obstacles (atoms)~\cite{vonasekphd}.
It is necessary to guide the growth of the tree by increasing the probability of sampling only around such Voronoi vertices that can be reached by the tree with a higher probability.
Such Voronoi vertices have to be located close to the tree.
Therefore, a subset $\VVA^i \subseteq \VV^i$ of the Voronoi vertices that are close to the tree is maintained (Alg.~\ref{alg::update}).
A Voronoi vertex $v \in \VV^i$ is considered as active if the distance to its nearest node in the tree is less than $\da$, but larger than $\db$.
After the update of $\VVA^i$, the tree attempts to expand towards them (Alg.~\ref{alg::main}, line~\ref{alg::main::d}--\ref{alg::main::e}).
This expansion is not always successful, especially for distant Voronoi vertices, but it helps the tree to explore the void space.

@@

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{fig/caver3450-3700_colored}
\caption{\label{fig::caver34}
Tunnels detected in a part of MD using our method (RRT) in comparison to tunnels detected by CAVER.
Both static tunnels detected by CAVER and by our method are depicted in gray.
Then, colored bars show snapshots where a dynamic tunnel was detected by our algorithm.
The dynamic tunnel bars are colored according to the order in which a snapshot occurs in the dynamic tunnel.
It is visible that our method is able to extract many additional information about the void space than traditional static tunnels computed by CAVER.
}
\end{figure}
